\tool: Revisiting BadUSB with Type-C

### 2021-03-15 WOOT/Files/discussion.tex
Update
fix problem of mirror, USBc support

\subsection{Limitation}
There exist multiple limitations of \tool. To begin with, when \tool is attached, the victim's device may not be set to mirror the screen. Depending on the victim's settings, the \tool may be used as an extended monitor or not be enabled at all. Additionally, some smartphone vendors (e.g. Huawei and Smartisan) provide a Desktop Mode to users, which displays a desktop on external screen instead of mirroring. In these cases, \tool is either easily noticeable to the victim or disabled.  Apart from that, we also noticed that in most devices, when an external monitor is connected to the device, there will be notifications about the monitor. In iPad, there is a small blue icon on the notification bar. In Windows 10, there is a pop-up for user to select the functionality of the external monitor. In latter case of a pop-up, \tool can dismiss it by injecting keystrokes and mouse movements. But they are still noticeable by the victim. Also, it cannot be ignored that DisplayPort over \ac{USB} is not available on all devices. When selecting devices to test \tool, we find that many smartphones equipped with USB-C connectors do not support \ac{USB} 3.2 protocol. Such lack of support further limits \tool.
\begin{comment}
There exist multiple limitations of \tool.  To begin with, \tool can only gain
the information and control access of the host itself instead of external
hardware.  Consequently, as we introduced in the
Section~\ref{sec:countermeasures}, \tool can hardly bypass the defense
approaches that use external hardware for authorization.  Moreover, most of
the devices will prompt users to give authentication to the \ac{USB} devices or
select one of the functional modes after they are plugged in.  Though some of
such prompts are not conspicuous for non-experts, especially when \tool is
concealed within other functional hardware such as power banks \shuqing{If
there is experiment, add it here.}, the probability of whether users could get
aware that something unusual happens will increase with the existence of these
prompting messages.
\end{comment}
\subsection{Impact}

>>>>

\subsection{Limitation}
There exist multiple limitations of \tool. To begin with, when \tool is attached, the victim's device may not be set to mirror the screen. 
Depending on the victim's settings, the \tool may be used as an extended monitor or not be enabled at all. Additionally, some smartphone vendors (e.g. Huawei and Smartisan) provide a Desktop Mode to users, which displays a desktop on external screen instead of mirroring. 
Moreover, as mentioned in Section~\ref{sec:experiment}, \tool cannot directly obtain the information on the lock screen.
In these cases, \tool is either easily noticeable to the victim or disabled.  Apart from that, we also noticed that in most devices, when an external monitor is connected to the device, there will be notifications about the monitor. In iPad, there is a small blue icon on the notification bar. In Windows 10, there is a pop-up for user to select the functionality of the external monitor. In latter case of a pop-up, \tool can dismiss it by injecting keystrokes as described in Section~\ref{subsec:attack_init}. But they are still noticeable by the victim. Also, it cannot be ignored that DisplayPort over \ac{USB} is not available on all devices. When selecting devices to test \tool, we find that many smartphones equipped with USB-C connectors actually do not support \ac{USB} 3.x protocol. There is a incomplete list of devices that support DisplayPort over \ac{USB}~\cite{usbclist} Most vendors like Huawei and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones. But there also exists vendor like Xiaomi who does not support \ac{USB} 3.x protocol at all.

\begin{comment}
There exist multiple limitations of \tool.  To begin with, \tool can only gain
the information and control access of the host itself instead of external
hardware.  Consequently, as we introduced in the
Section~\ref{sec:countermeasures}, \tool can hardly bypass the defense
approaches that use external hardware for authorization.  Moreover, most of
the devices will prompt users to give authentication to the \ac{USB} devices or
select one of the functional modes after they are plugged in.  Though some of
such prompts are not conspicuous for non-experts, especially when \tool is
concealed within other functional hardware such as power banks \shuqing{If
there is experiment, add it here.}, the probability of whether users could get
aware that something unusual happens will increase with the existence of these
prompting messages.
\end{comment}
\subsection{Impact}

### 2021-03-15 WOOT/Files/experiment.tex
fix problem of mirror, USBc support

\subsection{Attack Initialization}
After the \tool is plugged into the victim's device, there is an initialization process to make sure the \tool is able to carry out subsequent attack.
\begin{itemize}
	\item \textbf{Screen Mirror}:
		During our experiment, we noticed that some devices do not mirror their screen to our \tool by default. In this case, \tool will inject a sequence of keystrokes and mouse movements to set the victim's device into mirror their screen. For example, in Windows 10, \tool can inject `Win+P' keystroke and a mouse click on the `Duplicate' option. However, as \tool is unable to obtain the screen during this process, this can only be performed blindly with a possibility of failure.
	\item \textbf{Dismiss Notification}:
		In our experiment, we found that some devices will notify the user the presence of an external screen. During our experiment, the following notifications were raised: 
		\begin{itemize}
		 \item On Lenovo Xiaoxin Pro 13, it raised a pop-up asking user to select the functionality of the external screen. 
		 \item On Huawei P30, it showed a status bar indicator and a persistent notification about the external monitor.
		 \item On iPad Pro (the third generation), it also showed a blue status bar indicator and a notification about \ac{USB} accessories if iPad is locked.
		\end{itemize}
		To avoid being discovered by the victim, \tool can inject keystrokes and mouse movements to dismiss some of these notifications. For example, in the first case, \tool is able to inject a sequence of mouse movements to set the screen at mirror mode to dismiss the pop-up.
\end{itemize}
\begin{comment}
\begin{table*}[]
	\begin{tabular}{|c|c|c|c|}
		\hline
		Device                                                               & Operating System                                                                                         & Notification              & Dismiss Action                                            \\ \hline
		\begin{tabular}[c]{@{}c@{}}Lenovo Xiaoxin Pro 13\\ 2020\end{tabular} & Windows 10 (OS Build 18363.1379)                                                                         & Pop-up                    & ``Win+P''-\textgreater{}Mouse click on `Duplicate' Option \\ \hline
		\multirow{2}{*}{HUAWEI P30 (ELE-AL00)}                               & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}EMUI 11.0.0.135(C00E128R2P5)\\ Android 10 based\end{tabular}} & Status bar indicator      & N/A                                                       \\ \cline{3-4}
		&                                                                                                          & Persistent notifications  & N/A                                                       \\ \hline
		\multirow{2}{*}{iPad Pro (3rd generation)}                           & \multirow{2}{*}{iOS 14.4 (Build 18D52)}                                                                  & Status bar indicator      & N/A                                                       \\ \cline{3-4}
		&                                                                                                          & Pop-up (only when locked) & N/A                                                       \\ \hline
	\end{tabular}
	\linebreak
	\caption{Notifications about \tool}
	\label{tab:notification}
\end{table*}
\end{comment}

@@

In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
2020}, a PC in Windows 10 \mbox{(OS Build 18363.1379)} with two \ac{USB} Type-C interfaces as the
target device. During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel. When first plugged in, the victim's devices raised a pop-up window asking victims what mode should the new screen be set to. \tool immediately injected a sequence of mouse movements and clicks to set itself as a mirror to the primary monitor. Thus we had successfully completed the attack initialization. Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulted in success. Compared to original BadUSB attacks like Rubber Ducky, our \tool can provide attackers real-time feedback which allows attackers to perform more accurate attacks.
%This also warned us that we need more thorough defense against such BadUSB
%attack.

>>>>

\subsection{Attack Initialization}
\label{subsec:attack_init}
After the \tool is plugged into the victim's device, there is an initialization process to make sure the \tool is able to carry out subsequent attack.
\begin{itemize}
	\item \textbf{Screen Mirror}:
		During our experiment, we noticed that some devices do not mirror their screen to our \tool by default. In this case, \tool will inject a sequence of keystrokes to set the victim's device into mirror their screen. In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject `Win+P' multiple times to switch between different modes for external display. In MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{`Command+F1'} keystroke to  set the monitor into mirroring the primary screen. However, if the victim has default  setting for external monitor display mode, \tool will have to try these keystroke repeatedly to set itself into mirroring the victim's screen. For example, in Ubuntu, if the default setting is to disable external screen, \tool needs to press `Win+P' four times while if the default setting is to extend the primary screen, \tool needs to press `Win+P' five times.
	\item \textbf{Dismiss Notification}:
		In our experiment, we found that some devices will notify the user the presence of an external screen. During our experiment, the following notifications were raised: 
		\begin{itemize}
		 \item On Lenovo Xiaoxin Pro 13, it raised a pop-up asking user to select the functionality of the external screen. 
		 \item On Huawei P30, it showed a status bar indicator and a persistent notification about the external monitor.
		 \item On iPad Pro (the third generation), it also showed a blue status bar indicator and a notification about \ac{USB} accessories if iPad is locked.
		\end{itemize}
		To avoid being discovered by the victim, \tool can inject keystrokes and mouse movements to dismiss some of these notifications. For example, in the first case, \tool is able to inject a sequence of mouse movements to set the screen at mirror mode to dismiss the pop-up.
\end{itemize}
\begin{comment}
\begin{table*}[]
	\begin{tabular}{|c|c|c|c|}
		\hline
		Device                                                               & Operating System                                                                                         & Notification              & Dismiss Action                                            \\ \hline
		\begin{tabular}[c]{@{}c@{}}Lenovo Xiaoxin Pro 13\\ 2020\end{tabular} & Windows 10 (OS Build 18363.1379)                                                                         & Pop-up                    & ``Win+P''-\textgreater{}Mouse click on `Duplicate' Option \\ \hline
		\multirow{2}{*}{HUAWEI P30 (ELE-AL00)}                               & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}EMUI 11.0.0.135(C00E128R2P5)\\ Android 10 based\end{tabular}} & Status bar indicator      & N/A                                                       \\ \cline{3-4}
		&                                                                                                          & Persistent notifications  & N/A                                                       \\ \hline
		\multirow{2}{*}{iPad Pro (3rd generation)}                           & \multirow{2}{*}{iOS 14.4 (Build 18D52)}                                                                  & Status bar indicator      & N/A                                                       \\ \cline{3-4}
		&                                                                                                          & Pop-up (only when locked) & N/A                                                       \\ \hline
	\end{tabular}
	\linebreak
	\caption{Notifications about \tool}
	\label{tab:notification}
\end{table*}
\end{comment}

@@

In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
2020}, a PC in Windows 10 \mbox{(OS Build 18363.1379)} and Ubuntu 20.04.2 LTS with two \ac{USB} Type-C interfaces as the
target device. During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel. When first plugged in, the victim's devices raised a pop-up window asking victims what mode should the new screen be set to. \tool immediately injected a sequence of mouse movements and clicks to set itself as a mirror to the primary monitor. Thus we had successfully completed the attack initialization. Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulted in success. Compared to original BadUSB attacks like Rubber Ducky, our \tool can provide attackers real-time feedback which allows attackers to perform more accurate attacks.
%This also warned us that we need more thorough defense against such BadUSB
%attack.
